Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-05-04 ApJ_submit_v4/response.txt

#
We have clarified the description as follows: "...were corrected for bias,
flat-fielding, and atmospheric extinction.  We determined extinction corrections
from linear, least-squares fits to seasonal plots of nightly differential
magnitudes versus air mass and computing the slope in magnitudes per airmass."

2. I understand the authors argument for not showing reference star time series. The only concern I had was if one of the reference stars was variable at the several percent level, and this variation was being diluted and influencing the photometry of the target star. In lieu of plots of the reference stars, a statement to this effect is just as good.

Likewise, I would like some clarification in Figure 1. Currently panel 3 (the phase plot) is in black and white, but it would be useful for the points to be colored by observing season or a gradient from min(time) to max(time), to be sure that the proposed period phases up between observing seasons and cycles. I would also like the y-axis of panel 2 to be changed so that the actual data can be seen better and that it's not scrunched up in the bottom of the plot. I'm particularly interested in what appears to be an equally high peak in the frequency spectrum next to the proposed rotation period, and how the authors decide which peak is the "true" rotation period (unless it's just the peak the matches the measured v sin(i)

#
None of the reference stars had significant variability. We added this statemetn
to the text.

Regarding the color-coding for panel 3: this is unecessary because the stellar
rotation period is very short compared to the observing season, so each season
has comparably good phase coverage of the rotation period.

We modified the y-axis scale in panel 2. It's true that both peaks in the
periodogram have very comparable strength (the periods are 1-year aliases of
each other), but as the referee correctly surmised the peak we chose is a better
match to the v sin(i). We added this clarification to the text.

@@

4. (optional) I thank the authors for adding a 100ppm scale bar on Figure 6. I still believe at least some of the sub-plots can have the same scale. For example, the 3rd and 4th panel on the top row and the 1st and 2nd panels on the bottom row are all almost identical to each other in scale. However, they are all slightly different, which doesn't seem necessary. While I believe enforcing the same scale for sub-plots that are already very close to each other will make the manuscript and presentation clearer, this is also optional.
#
We modified the axes so that spectra with symmetric phases (0.1 and 0.9, 0.2 and
0.8, etc. ) have the same y-limits.

5. (optional) I would prefer different wording in section 4.3 than the (added) "From a glance at Figure 8, the amplitude of the effect is ~100 ppm". The authors should be less colloquial and state "We estimated the amplitude of this effect by eye to be ~100 ppm" or something similar, such as "visual inspection". 
#
We reworded this sentence to state "By visual inspection of Figure 8, we estimated the amplitude of this effect to be about 100 ppm".

6. Nightside Spectrum: The authors have declined to fit a nightside spectrum at phase 0.9 to compare with their analysis with the spectrum at phase 0.1. This is fine, since the authors note that they are unable to constrain the C/O abundance or the metallicity significantly. However, the authors state the best fit spectrum has a non-inverted TP profile, which the authors imply is a robust statement.

If the authors do not wish to run a retrieval on phase 0.9, then at least some confidence interval should be assigned to the claim of a non-inverted temperature pressure profile on the night side of the planet. Is the spectrum also consistent with an inverted profile or can that be ruled out at some confidence? How "best" is the "best fit". This statement should be quantified. 
#
We calculated the drop in brightness temperature between the WFC3 blackbody fit
and a fit to the Spitzer 4.5 micron point at phase 0.9 (reported in Table 6).
The Spitzer temperature is cooler than the WFC3 temperature by 5.6 sigma.  This
value is a lower limit to the significance, because the brightenss temperatures
noted in the table also include the uncertainty in the stellar Teff (which
increases the error bar on absolute planet temperature but not the relative temperatures we
care about here). We note that the drop in brightness temperature is actually
stronger at phase 0.9 than it is at 0.1 (5.6 versus 2.7 sigma). Combined with
the retrieval we did for phase 0.1, this is conclusive evidence that the
nightside temperature profile is not inverted.

We added this quantification to the text.

### 2018-05-04 arxiv_v1/ms.tex
acknowledgment from Mike
correct zhang reference

For all three phase curves, the hotspot offset is consistent with zero degrees, which could indicate a small ratio of radiative to advective timescales (the incident flux is reradiated to space faster than it is advected around to the nightside). Fast radiative timescales are predicted at high temperatures, and small hotspot offsets are also observed for other very hot Jupiters \citep{perez13, komacek16, komacek17}.  The measured offsets are inconsistent with the trend reported in \cite{zhang17}, which predicts the hotspot offset increases with planet temperature for irradiation temperatures greater than 3410 K. The \cite{zhang17} model predicts an eastward hotspot offset of $4.5^\circ$ for WASP-103b, which is significantly larger than observed, hinting at diversity in the circulation patterns of the hottest planets.  The phase curve amplitudes are large (near 0.8 - 0.9), as expected for an atmosphere with inefficient heat redistribution. In \S\,\ref{sec:gcm} we compare these results to expectations from 3D GCMs.

@@

\acknowledgments
Support for \textit{HST} program GO-15050 was provided by NASA through a grant from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555. Support for \textit{Spitzer} program 11099 was provided by NASA through an award issued by JPL/Caltech.  The data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST) and the NASA/IPAC Infrared Science Archive. The Infrared Science Archive is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.  This work also made use of the Python packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}. The authors are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan. We also thank the organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg Atmospheres of Disks and Planets meeting for facilitating productive discussion and collaboration.  J.L.B. acknowledges support from the David and Lucile Packard Foundation.  J.M.D. acknowledges support from the European Research Council (ERC) under the programme Exo-Atmos (grant agreement no. 679633). G.W.H. and M.H.W. also acknowledge long-term support from Tennessee State University and the State of Tennessee through its Centers of Excellence Program.

 \newcommand{\noop}[1]{}
\begin{thebibliography}{}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\providecommand{\url}[1]{\href{#1}{#1}}

\bibitem[{Adcroft {et~al.}(2004)Adcroft, Campin, Hill, \&
  Marshall}]{Adcroft2004}
Adcroft, A., Campin, J.-M., Hill, C., \& Marshall, J. 2004, Monthly Weather
  Review, 132, 2845.
\newblock \url{https://doi.org/10.1175/MWR2823.1}

@@

>>>>

For all three phase curves, the hotspot offset is consistent with zero degrees,
which could indicate a small ratio of radiative to advective timescales (the
incident flux is reradiated to space faster than it is advected around to the
nightside). Fast radiative timescales are predicted at high temperatures, and
small hotspot offsets are also observed for other very hot Jupiters
\citep{perez13, komacek16, komacek17}.  The measured offsets are inconsistent
with the trend reported in \cite{zhang18}, which predicts the hotspot offset
increases with planet temperature for irradiation temperatures greater than 3410
K. The \cite{zhang18} model predicts an eastward hotspot offset of $4.5^\circ$ for WASP-103b, which is significantly larger than observed, hinting at diversity in the circulation patterns of the hottest planets.  The phase curve amplitudes are large (near 0.8 - 0.9), as expected for an atmosphere with inefficient heat redistribution. In \S\,\ref{sec:gcm} we compare these results to expectations from 3D GCMs.

@@

\acknowledgments
Support for \textit{HST} program GO-15050 was provided by NASA through a grant
from the Space Telescope Science Institute, which is operated by the Association
of Universities for Research in Astronomy, Inc., under NASA contract NAS
5-26555. Support for \textit{Spitzer} program 11099 was provided by NASA through
an award issued by JPL/Caltech.  The data presented in this paper were obtained
from the Mikulski Archive for Space Telescopes (MAST) and the NASA/IPAC Infrared
Science Archive. The Infrared Science Archive is operated by the Jet Propulsion
Laboratory, California Institute of Technology, under contract with the National
Aeronautics and Space Administration.  This work also made use of the Python
packages  SciPy and NumPy \citep{jones_scipy_2001, van2011numpy}. The authors
are grateful for helpful conversations with Caroline Morley, Thomas Beatty, Ming
Zhao, Kim Star Cartier, Hannah Diamond-Lowe, and Nick Cowan. We also thank the
organizers of the 2016 Santa Cruz Kavli Summer Program and the 2017 Ringberg
Atmospheres of Disks and Planets meeting for facilitating productive discussion
and collaboration.  J.L.B. acknowledges support from the David and Lucile
Packard Foundation.  J.M.D. acknowledges support from the European Research
Council (ERC) under the programme Exo-Atmos (grant agreement no. 679633). G.W.H.
and M.H.W. also acknowledge long-term support from Tennessee State University
and the State of Tennessee through its Centers of Excellence Program. M.R.L.
acknowledges NASA XRP grant NNX17AB56G for partial support of the theoretical
interpretation of the data, as well as the ASU Research Computing staff for support with the Saguaro and Agave compute clusters.

\newcommand{\noop}[1]{}
\begin{thebibliography}{}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{Adcroft {et~al.}(2004)Adcroft, Campin, Hill, \&
  Marshall}]{Adcroft2004}
Adcroft, A., Campin, J.-M., Hill, C., \& Marshall, J. 2004, Monthly Weather
  Review, 132, 2845

@@

\bibitem[{{Zhang} {et~al.}(2018){Zhang}, {Knutson}, {Kataria}, {Schwartz},
  {Cowan}, {Showman}, {Burrows}, {Fortney}, {Todorov}, {Desert}, {Agol}, \&
  {Deming}}]{zhang18}
{Zhang}, M., {Knutson}, H.~A., {Kataria}, T., {et~al.} 2018, \aj, 155, 83
